Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-10-06 formally.tex
updating movement erasure statements to actually fit the judgemental forms. these imply the lemmas that were stated before, as well as pin and a few other things. they also match the form of the other theorems given more closely, so i like them much better. #3
mentioning structural props close #12

Our overview below omits certain ``uninteresting'' details. The supplement
includes the complete collection of rules, in definitional order. These
rules, along with the proofs of two key metatheorems, have been mechanized
in Agda \cite{norell:thesis}, also in the supplement. We will summarize
this effort in Sec. \ref{sec:mech}.

@@

The rules above are numerous and fairly uninteresting. That makes them
quite hazardous -- we might make a mistake absent-mindedly. One check
against this is to prove a lemma that establishes that movement actions
move the cursor but do not change the cursor erasure.

@@

  \item If $\performMove{\zexp}{\aMove{\delta}}{\zexp'}$ then
    $\removeSel{\zexp}=\removeSel{\zexp'}$.
\end{enumerate}
\end{theorem}
\noindent Theorem \ref{lemma:movement-erasure} is useful also in that the
relevant cases of Theorem \ref{thrm:actsafe} are straightforward by its
application.

>>>>

Our overview below omits certain ``uninteresting'' details. The supplement
includes the complete collection of rules, in definitional order. These
rules, along with the proofs of all of the metatheorems listed, have been
mechanized in Agda \cite{norell:thesis}, also in the supplement. All the
judgements that mention contexts described below enjoy the standard
structural properties of weakening, contraction, and exchange, and this too
is proven in the mechanization. We will summarize this effort in
Sec. \ref{sec:mech}.

@@

The rules above are numerous and fairly uninteresting. That makes them
quite hazardous -- we might make a mistake absent-mindedly. One check
against this is to prove that establishes that movement actions do not
change the cursor erasure, as in Theorem \ref{lemma:movement-erasure}.

@@

  \item If
    $\performSyn{\hGamma}{\zexp}{\htau}{\aMove{\delta}}{\zexp'}{\htau}$
    then $\removeSel{\zexp}=\removeSel{\zexp'}$.

  \item If $\performAna{\hGamma}{\zexp}{\htau}{\aMove{\delta}}{\zexp'}$
    then $\removeSel{\zexp}=\removeSel{\zexp'}$.

\end{enumerate}
\end{theorem}
\noindent Theorem \ref{lemma:movement-erasure} is useful also in that the
relevant cases of Theorem \ref{thrm:actsafe} are straightforward by its
application.
